Combining genomic prediction with citizen science for crop improvement and early selection in durum wheat

### 2019-06-13 manuscript/manuscript.Rmd
13062019

Kauê de Sousa^1,2,^*, Matteo Dell’Acqua^3^, Jacob van Etten^2^, Carlo Fadda^4^, Yosef Gebrehawaryat^4^, Jean-Luc Jannink^5,6^, Dejene Mengistu^7^, Mario Enrico Pè^3^, [… add others], Svein Ø. Solberg^1^  
^1^ Department of Agricultural Sciences, Inland Norway University of Applied Sciences, 2318 Hamar, Norway  
^2^ Bioversity International, Costa Rica Office, 30501 Turrialba, Costa Rica   
^3^ Scuola Superiore Sant’Anna, Institute of Life Sciences, 56124 Pisa, Italy  
^4^ Bioversity International, Ethiopia Office, 1000 Addis Ababa, Ethiopia  
^5^ College of Agriculture and Life Sciences, Cornell University, 14853 Ithaca, USA  
^6^ Agricultural Research Service, United States Department of Agriculture, 148532901, Ithaca, USA  
^7^ Bioversity International, Nepal Office, 3055 Kathmandu, Nepal

>>>>

Kauê de Sousa^1,2^, Jacob van Etten^2^, Carlo Fadda^3^, Yosef Gebrehawaryat^3^, Jean-Luc Jannink^4,5^, Basazen Fantahun Lakew^6^, Dejene Mengistu^7^, Svein Ø. Solberg^1^, Mario Enrico Pè^6^, Jesse Poland^8^, [… add others], Melfa and Workaye Farmer Community, Matteo Dell’Acqua^6[*]^  
^1^ Department of Agricultural Sciences, Inland Norway University of Applied Sciences, 2318 Hamar, Norway ^2^ Bioversity International, Costa Rica Office, 30501 Turrialba, Costa Rica   
^3^ Bioversity International, Ethiopia Office, 1000 Addis Ababa, Ethiopia  
^4^ College of Agriculture and Life Sciences, Cornell University, 14853 Ithaca, USA  
^5^ Agricultural Research Service, United States Department of Agriculture, 148532901, Ithaca, USA  
^6^ Scuola Superiore Sant’Anna, Institute of Life Sciences, 56124 Pisa, Italy  
^7^ Bioversity International, Nepal Office, 3055 Kathmandu, Nepal 
^8^ Kansas State University, Kansas, USA
^[*]^To whom correspondence must be addressed <m.dellacqua@santannapisa.it>
